---
title: "Analysis of Regex on So"
author: "Miles McBain"
date: "2018-04-21"
output: html_document
---

# Start

```{r }
library(stackr)
library(tidyverse)
library(tidytext)
library(lubridate)
regex_faq <- read_rds("./data/all_faqs.Rds")

coocurring_tags <-
  regex_faq %>%
  select(tags) %>%
  unnest_tokens(tag, tags) %>%
  filter(tag != "regex")

tag_counts <-
  coocurring_tags %>%
  count(tag, sort = TRUE)

print(tag_counts, n = 300)

names(regex_faq)
```

# observations:
R is the 15th most commonly coocurring tag. The tags do not give much insight since they mostly refer to programming environments. Although we do see some concepts ranked highly:

```{r}
regex_concepts <-
   c("replace",
   "match",
   "parsing", 
   "validation",
   "split",
   "rewrite",
   "negation",
   "escaping",
   "search",
   "greedy",
   "lookarounds",
   "substring",
   "whitespace")

 tag_counts %>%
      filter(tag %in% regex_concepts) %>%
      ggplot(aes(x = fct_reorder(tag,n), y = n)) +
        geom_col()
```

## Weighted tag analysis
A linear model might be an interesting way to model the concept importance:

```{r}
tags_id_view_list <-
  regex_faq %>%
  select(question_id, view_count, tags) %>%
  unnest_tokens(tag, tags) %>%
  mutate(count = 1) 

concept_tags_dtm <-
  tags_id_view_list %>%
  filter(tag %in% regex_concepts) %>%
  cast_dtm(question_id, tag, count) %>%
  as.matrix()

tidy_concept_tags <- 
  tidy(concept_tags_dtm) %>%
  rename(question_id = .rownames) %>%
  mutate(question_id = as.integer(question_id))

regex_faq %>%
  select(view_count, question_id) %>%
  left_join(tidy_concept_tags) %>%
  mutate_all(.funs = funs(replace_na), 0) %>%
  select(-question_id) %>%
  lm(view_count ~ ., .) %>%
  summary()
```
### Observations
R^2 is rubbish but model does indicate some tags are associated with higher counts. It would be interesting to try a model with all tags.

## Model popular tags + concepts
Here I try a concept tag model for the log of views, controlling for popular framework tags and question age.

```{r}
faq_views_days <-
  regex_faq %>%
  select(question_id, view_count, creation_date) %>%
  mutate(days_since_creation = interval(creation_date,
                                        ymd_hms("2018-04-21 12:00:00")) / days(1)) %>%
  select(-creation_date)

popular_tags <-
  tag_counts$tag[1:30]

tidy_populr_concept_tags <-
  tags_id_view_list %>%
  filter(tag %in% union(regex_concepts, popular_tags)) %>%
  cast_dtm(question_id, tag, count) %>%
  as.matrix() %>%
  tidy() %>%
  rename(question_id = .rownames) %>%
  mutate(question_id = as.integer(question_id))

tag_model <- 
  faq_views_days %>%
  left_join(tidy_populr_concept_tags) %>%
  mutate_all(.funs = funs(replace_na), 0) %>%
  mutate(match = as.integer(match | matching)) %>%     #merge match columns
  select(-question_id, -matching) %>%
  lm(log(view_count) ~ ., .) # updated to log-response

summary(tag_model)

tidy(tag_model, conf.int = TRUE) %>%
  mutate(concept = term %in% regex_concepts) %>%
  ggplot(aes(x = estimate, y = fct_reorder(term, conf.high), colour = concept)) +
    geom_point() +
    geom_errorbarh(aes(xmin = conf.low,
                       xmax = conf.high)) +
  ggtitle("Esitmated effect of tag presence on Stack Overflow FAQ views",
          subtitle = "Controlling for popular frameworks and question age") +
  xlab("Estimated effect on log(views) with 95% CI") +
  ylab("FAQ Tags coocurring with 'regex'")

```

### Observations
Controlling for question age and popular framework effects, there is still
evidence that the following regex concept tags are associated with higher
question views: negation, lookarounds, validation, greedy, and whitespace.

The signs of the framework tags are mostly negative, which seemed odd, until I
realised that a specific framework tag splinters the potential viewership. It
makes sense that general regular expression questions get more views within the
regex tag. I also tried fitting a set of tag interactions with days since
creation. This didn't change the overall story much, the same concept tags as
before had strong interaction effects, suggesting they grow faster.

The diagnostics of the model are all poor, but we know we have unobserved
variables creating noise. This is not meant to be a predictive model - its use
is comparing the strength if tag effects.

note: I noticed 'match' and 'matching' as separate tags, and so I decided to
merge the tags.

### Log Views Model

The log(view_count) model fits a lot better, with saner diagnostics and this
makes sense given the distribution of views which has a long upper tail.

Under this model the ranking of concerns is different: whitespace, escaping,
validation, substring, match, lookarounds, rewrite, negation, greedy, replace,
parsing.

Intuitively this ranking feels better to me. Whitespace and escaping are
definitely common concerns.


## A look at R questions
Regex FAQ's with R tags ranked in descending order of views:

```{r}
### a look at some of the R questions
regex_faq %>%
  filter(grepl("\b\r\\b|\\br-faq,", tags)) %>%
  arrange(desc(view_count)) %>%
  select(title, link, view_count)


 ###

```
## Regex + R tag pair
Here I filter down to R tags within the regex faqs to see what the other tags and titles are.

```{r}
r_cotags_counts <-
  regex_faq %>%
  filter(grepl("\\br\\b|\\br-faq\\b", tags)) %>%
  select(question_id, view_count, tags) %>%
  unnest_tokens(tag, tags) %>%
  filter(!(tag %in% c("r", "r-faq", "regex"))) %>%
  count(tag) %>%
  arrange(desc(n)) %>%
  print(n = 50)

```

The most frequently occurring conceptual tags are: string, gsub, grep, split, stringr, strsplit, replace, date, matching, substring.

'string' is the highest but is not descriptive. I decided to drill into this group more.

### R string tag
```{r}
string_r_tags <-
  regex_faq %>%
  arrange(desc(view_count)) %>%
  filter(map_lgl(strsplit(x = tags, split = ","),
                 ~all(c("r", "string") %in% .))) %>%
  select(title, link)
```

It seems 'string' is a catch all category for splitting, extraction - numbers,
substitution and removal - particularly dealing with whitespace.

### R Tag Topic Modelling
The R cotags were not very descriptive so I did not think the linear model
approach from earlier would provide much insight. Topic modelling was
investigated. A question immediately arising is what should topic modelling be
done on? The title? The question text? Both?

#### Title Topics

```{r}
library(tm)
library(topicmodels)

stop_words

### let's try just the titles.
title_text_tfidf <- 
  regex_faq %>%
  filter(grepl(x = tags, pattern = "\\br\\b|\\br-faq\\b")) %>%
  select(question_id, title) %>%
  unnest_tokens(title_word, title) %>%
  count(question_id, title_word) %>%
  bind_tf_idf(title_word, question_id, n) 

title_text_matix <-
  title_text_tfidf %>%
  filter(!(title_word %in% stop_words$word)) %>%
  cast_dtm(question_id, title_word, n)


title_lda <- LDA(title_text_matix, k =6)

tidy_title_lda <- tidy(title_lda)

### top n per topic
tidy_title_lda %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>%
  print(n = 60)
```
##### Observations

The choice of k = 6 was arbitrary but it does seem like there are some topics
that are distinct, and familiar. 4 and 6 are my favourites. I'd label them
'search' and 'extract' respectively.

#### Title + Text topics
I decided to pool the title and the question text for another round of topic modelling.

```{r}
regex_faq
```

# TODO

* Analysis of regex, R tag pair.
* Text analysis/topic modelling of Question content.
 
 
